Estimating SARS-CoV-2 transmission in England from randomly sampled prevalence surveys

### 2024-02-02 transmission.tex
format textcite

\todo[inline]{
    Lit review to go in introduction chapter, framing the whole thesis because it is important in understanding the motivation for the whole work.
    Would include \textcites{mccabeCISincidence}{abbottCISincidence} on backcalculation. Also Toffe?
    As well as the literature on mechanistic models using REACT and CIS I have previously circulated.
}
\section{Data} \label{transmission:sec:data}

@@

I take information on the contact rates, $\kappa_{aa'}(t)$, from several data sources, using the methodology of \textcites{vanleeuwenTime}{vanleeuwenAugmenting}.
%; these estimates have been used for previous modelling of the COVID-19 pandemic~\autocite{vanleeuwenTime,birrellRealtime}.
% These start with estimates of contact in each setting, based on \textcite{vanleeuwenAugmenting}.
This method starts with pre-pandemic baseline estimates of: $\kappa_{aa'}$ from the POLYMOD study~\autocite{mossongSocial}, and time use from the UK Time Use Survey (UKTUS)~\autocite{UKTUS}.
POLYMOD asked a representative sample of the UK population about the contacts they make each day, including information on each contact's age and location (home, work, school, leisure, transport, or other).
UKTUS asked a representative sample of the UK population about how much time they spent doing various activities (\eg shopping and spending time at home) each day.
\Textcite{vanleeuwenAugmenting} combined these two datasets to estimate the rate of contacts between age groups during each activity.
\Textcite{birrellRealtime} then modify these contact rates based on measured changes in time use during the pandemic.
These changes are measured using Google mobility data~\autocite{googleCOVID19} and school attendance data~(unpublished).
Google mobility data is based on the location of Android users over time, relative to a pre-pandemic baseline.
The mobility and school data are averaged over a week then used to down or up-weight the number of contacts in each setting, before combining contacts across settings to form $\kappa_{aa'}(t)$.
$\kappa_{aa'}(t)$ is assumed to be piecewise constant, changing only at the start of each week.
For further details see \textcite{vanleeuwenAugmenting} and \textcite[supplementary material]{birrellRealtime}.

>>>>

\todo[inline]{
    Lit review to go in introduction chapter, framing the whole thesis because it is important in understanding the motivation for the whole work.
    Would include \textcite{mccabeCISincidence,abbottCISincidence} on backcalculation. Also Toffe?
    As well as the literature on mechanistic models using REACT and CIS I have previously circulated.
}
\section{Data} \label{transmission:sec:data}

@@

I take information on the contact rates, $\kappa_{aa'}(t)$, from several data sources, using the methodology of \textcite{vanleeuwenTime,vanleeuwenAugmenting}.
%; these estimates have been used for previous modelling of the COVID-19 pandemic~\autocite{vanleeuwenTime,birrellRealtime}.
% These start with estimates of contact in each setting, based on \textcite{vanleeuwenAugmenting}.
This method starts with pre-pandemic baseline estimates of: $\kappa_{aa'}$ from the POLYMOD study~\autocite{mossongSocial}, and time use from the UK Time Use Survey (UKTUS)~\autocite{UKTUS}.
POLYMOD asked a representative sample of the UK population about the contacts they make each day, including information on each contact's age and location (home, work, school, leisure, transport, or other).
UKTUS asked a representative sample of the UK population about how much time they spent doing various activities (\eg shopping and spending time at home) each day.
\Textcite{vanleeuwenAugmenting} combined these two datasets to estimate the rate of contacts between age groups during each activity.
\Textcite{birrellRealtime} then modify these contact rates based on measured changes in time use during the pandemic.
These changes are measured using Google mobility data~\autocite{googleCOVID19} and school attendance data~(unpublished).
Google mobility data is based on the location of Android users over time, relative to a pre-pandemic baseline.
The mobility and school data are averaged over a week then used to down or up-weight the number of contacts in each setting, before combining contacts across settings to form $\kappa_{aa'}(t)$.
$\kappa_{aa'}(t)$ is assumed to be piecewise constant, changing only at the start of each week.
For further details see \textcite{vanleeuwenAugmenting} and \textcite[supplementary material]{birrellRealtime}.
